Discovery of s-process stars in the LAMOST survey

### 2018-02-06 article/ms.tex
text  done

We find $<2$\,\% of our Barium stars show sodium enhancement, contrary to previous studies \citep[e.g.,][]{decastro2016}. We also note that the 5 sodium-enhanced Barium stars all have $\log{g} \approx 3$, not at lower $\log{g}$ values as might be expected if low $\log{g}$ values systematically contributed to higher [Na/Fe] abundance ratios. It's important to note sodium enhancement can occur due to the presence of interstellar dust. Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2 of 5 of these stars have strong ($\approx$0.35) E(B-V) values, suggesting that the flux residuals around the Na doublet are due to interstellar absorption. However, 3 exhibit low ($\approx$0.045) E(B-V) values, indicating the enhancement is more likely due to stellar absorption. These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 3 Barium candidates, but importantly, sodium enhancement is by no means ubiquitous in Barium stars.

@@

The final surface s-process index [hs/ls], shown in \citet{cristallo2015} and illustrated in Figure \ref{fig:figure3}, highlights the relationship between [hs/ls] yields and the mass of AGB stars. The Salpeter IMF predicts the majority of stars in the Milky Way will be at lower mass, and as predicted the [hs/ls] values of our Barium stars approximately fit the lower mass yields as seen in Figure \ref{fig:figure3}. Our Barium candidates not fitting this relationship represent the possibly more massive AGB stars (intrinsic Barium stars) within our sample.

@@

Despite our noisy estimates of [Ba/Fe] and [Sr/Fe] from LAMOST spectra, comparisons with AGB yields indicate that our sample is consistent with a bottom-heavy initial mass function. We encourage follow-up observations with high-resolution spectrographs in order to precisely measure neutron-capture abundances (including [hs/ls] ratios). These data would permit the most detailed comparisons with AGB star yields ever considered.

>>>>

We find $<2$\,\% of our Barium stars show sodium enhancement, contrary to previous studies \citep[e.g.,][]{decastro2016}. We also note that the 5 sodium-enhanced Barium stars all have $\log{g} \approx 3$, not at lower $\log{g}$ values as might be expected if low $\log{g}$ values systematically contributed to higher [Na/Fe] abundance ratios. It's important to note sodium enhancement can occur due to the presence of interstellar dust. Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2 of 5 of these stars have E(B-V)$\approx$ 0.35, suggesting that the flux residuals around the Na doublet are due to interstellar absorption. However, 3 exhibit low ($\approx$0.045) E(B-V) values, indicating the enhancement is more likely due to stellar absorption. These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 3 Barium candidates, but importantly, sodium enhancement is by no means ubiquitous in Barium stars.

@@

The final surface s-process index [hs/ls], shown in \citet{cristallo2015} and illustrated in Figure \ref{fig:figure3}, highlights the relationship between [hs/ls] yields and the mass of AGB stars. The Salpeter initial mass function (or any bottom-heavy initial mass function) predicts the majority of stars in the Milky Way will have lower masses, and as predicted the [hs/ls] values of our Barium stars approximately fit the lower mass yields as seen in Figure \ref{fig:figure3}. Our Barium candidates not fitting this relationship represent the possibly more massive, and expectedly rarer, AGB stars (intrinsic Barium stars) within our sample.

@@

Despite our noisy estimates of [Ba/Fe] and [Sr/Fe] from LAMOST spectra, comparisons with AGB yields indicate that our sample is consistent with a bottom-heavy initial mass function. We encourage follow-up observations with high-resolution spectrographs in order to precisely measure a full suite of neutron-capture abundances. These data would permit the most detailed comparisons with AGB star yields ever considered.
